worldmap

### 2021-06-30 analysis/visualization.Rmd
Add historgrams of the duration of timeseries.

```{r}
#get rarefyid centers
included_ids <- pins::pin_get("model-data", board = "github") %>%
  select(rarefyID, taxa, climate, realm) %>%
  distinct() %>% 
  mutate(rarefyID = str_replace_all(rarefyID, pattern = "_bird", ""), 
  rarefyID = str_replace_all(rarefyID, pattern = "_mamm", ""))

study_data <- pins::pin_get("rarefyID-cell-centre", board = "github") %>%
  inner_join(included_ids)

map_data("world") %>%
  ggplot(aes(long, lat, group = group)) +
  geom_polygon(fill = "white", colour = "grey") + 
  coord_map(xlim=c(-180,180), ylim=c(-57, 90)) +
  geom_point(data = study_data, aes(rarefyID_x, rarefyID_y, color = taxa), alpha = 0.5, inherit.aes = FALSE) +
  ggthemes::theme_map()

@@

>>>>

```{r}
#library(forcats)

#get rarefyid centers
included_ids <- pins::pin_get("model-data", board = "github") %>%
  select(rarefyID, taxa, climate, realm, duration) %>%
  distinct() %>% 
  mutate(rarefyID = str_replace_all(rarefyID, pattern = "_bird", ""), 
  rarefyID = str_replace_all(rarefyID, pattern = "_mamm", ""))

study_data <- pins::pin_get("rarefyID-cell-centre", board = "github") %>%
  inner_join(included_ids) #%>%
  #mutate(taxa = as.factor(taxa), taxa = fct_relevel(taxa, "Birds"))

study_map <- map_data("world") %>%
  ggplot(aes(long, lat, group = group)) +
  geom_polygon(fill = "white", colour = "grey") + 
  coord_map(xlim=c(-180,180), ylim=c(-57, 90), projection = "mercator") +
  geom_point(data = study_data, aes(rarefyID_x, rarefyID_y, color = taxa), alpha = 0.3, inherit.aes = FALSE) +
  ggthemes::theme_map() +
  theme(legend.title  = element_blank())

@@

```{r}
duration_hist <- study_data %>% 
  #filter(taxa == "Birds") %>%
  ggplot(aes(duration)) + 
  geom_histogram(aes(fill = taxa)) + 
  theme_classic() + 
  facet_wrap(~taxa, scales = "free") +
  theme(strip.background = element_blank(), strip.text = element_blank(),
        legend.position = "none")

plot_grid(study_map, duration_hist, labels = "AUTO", nrow = 2, align = 'vh', hjust = -1, axis = "l", scale = c(1,0.9), rel_heights = c(2, 1))

ggsave2(here::here("figures/study_map_hist.jpeg"))
```
